\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}

\title{NOUS: A Self-Improving Large Language Model Framework\\for Consumer Hardware}

\author{
  \IEEEauthorblockN{George David Tsitlauri}
  \IEEEauthorblockA{
    \textit{Dept. of Informatics \& Telecommunications}\\
    \textit{University of Thessaly, Greece}\\
    gdtsitlauri@gmail.com
  }
}

\begin{document}

\maketitle

\begin{abstract}
NOUS (Neural Omnidirectional Understanding System) is a local, consumer-hardware
research framework for post-generation LLM self-improvement. It combines a
quantized 3B-class model with nine modules for self-critique, memory,
knowledge-graph updates, hallucination control, adversarial self-play, and
execution-based code critique. The repository's main contribution is a complete
implementation of this loop together with a benchmark harness that can export
per-seed and averaged results to JSON and CSV. In the current working copy, the
historical benchmark outputs are not committed, so this paper intentionally
focuses on the implemented architecture and the hardened evaluation pipeline
rather than repeating unsupported headline numbers from unsaved local runs.
\end{abstract}

\begin{IEEEkeywords}
self-improving AI, large language models, autonomous learning, self-critique, knowledge graph, consumer hardware
\end{IEEEkeywords}

\section{Introduction}

Most self-improving language-model research assumes either server-class hardware
or proprietary API access. NOUS investigates a different question: how much of
that loop can be implemented and audited on constrained consumer hardware.

The repository is built around a local quantized model and a modular improvement
loop that can:
\begin{itemize}
  \item critique and revise its own answers,
  \item maintain memory across interactions,
  \item grow a lightweight knowledge graph,
  \item perform adversarial self-review,
  \item use execution-based feedback for code tasks.
\end{itemize}

\section{Architecture}

NOUS consists of nine major modules:
\begin{enumerate}
  \item Self-Critique
  \item Knowledge Graph
  \item Curiosity Engine
  \item Memory
  \item Meta-Learning
  \item Hallucination Reduction
  \item Adversarial Self-Play
  \item Reasoning and Logic
  \item Code Understanding with execution-based critique
\end{enumerate}

The key practical idea is that code tasks are treated differently from generic
language tasks. Instead of only asking the model to verbally critique code, the
repository can execute candidate programs and feed concrete error signals back
into the refinement loop.

\section{Evaluation Pipeline}

The benchmark harness in \texttt{experiments/run\_full\_paper.py} supports:
\begin{itemize}
  \item multiple seeds,
  \item multiple benchmarks,
  \item baseline versus NOUS comparisons,
  \item an ablation path over key modules,
  \item structured export to JSON and CSV.
\end{itemize}

The current hardening pass extends the persistence layer so that future runs
write:
\begin{itemize}
  \item \texttt{results/full\_paper\_results.json},
  \item \texttt{results/benchmarks/per\_seed\_scores.csv},
  \item \texttt{results/benchmarks/averaged\_scores.csv},
  \item \texttt{results/ablation/ablation\_summary.csv}.
\end{itemize}

\section{Current Artifact Status}

The implementation and benchmark harness are present in the repository.
Historical benchmark outputs from earlier local runs are not preserved in the
checked-in \texttt{results/} directory. That distinction matters.

It means the repository currently supports the following claims:
\begin{itemize}
  \item the NOUS architecture is implemented,
  \item the benchmark harness is implemented,
  \item future benchmark claims can be tied to explicit JSON/CSV artifacts.
\end{itemize}

It does \emph{not} currently justify restating unsaved benchmark numbers as
archival evidence.

\section{Why The Repository Still Matters}

The absence of committed benchmark exports does not reduce NOUS to an empty idea.
The codebase contains real modules, benchmark classes, a model wrapper, memory
components, and execution-based critique logic. The repair performed in this pass
addresses the actual failure mode: artifact persistence and evidence hygiene.

\section{Limitations}

\begin{itemize}
  \item Benchmark outputs must be regenerated before strong empirical claims are reused externally.
  \item Small local models are noisy self-critics and can produce unstable scores.
  \item Consumer-hardware feasibility does not by itself imply strong benchmark leadership.
\end{itemize}

\section{Conclusion}

NOUS remains a serious cognitive/LLM research repository because the architecture
and evaluation harness are implemented and inspectable. The main gap was not a
missing system but a missing artifact trail. With structured result exports now
wired into the benchmark runner and the README/paper reframed around saved
evidence only, the repository is in a much stronger and more credible state.

\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}
\bibitem{brown2020gpt3}
T.~B. Brown et al., ``Language models are few-shot learners,'' in \textit{NeurIPS}, 2020.
\bibitem{touvron2023llama}
H.~Touvron et al., ``LLaMA: Open and efficient foundation language models,'' \textit{arXiv:2302.13971}, 2023.
\end{thebibliography}

\end{document}
